Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-03 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
Adding more figure annotations and discussion

\begin{figure}[htb]
\centering
\includegraphics[width=0.35\textwidth,angle = -90]{ACResponseB1}
\caption{Simulated AC Response for Board 1}
\label{fig:simACBoard1}
\end{figure}

@@

@@

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Probed_Input_N10_N240_NoSeriesResistance}
\caption{Simulated Risetimes for Input pulse, $10^{th}$ node, and the $240^{th}$ node}
\label{fig:probedNoResistance}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSquareResponseB1.png}
\caption{Risetime Measurement from Board 1 (L=56nH)}
\label{fig:MeasuredSquareGeneric}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSpectrum.png}
\caption{}
\label{fig:MeasSpec}
\end{figure}

@@

@@

\section{ Model Accuracy/ Predictions }
Under Construction: Using this section for generating bibliography for the the
time being. We will work on predictions and further flesh things out during the
next revision.
\cite{ould2011circuit} \cite{distributedAnalogPhase},\cite{ellinger2003varactor},\cite{lee2012nonlinear},\cite{UltraCompact},\cite{EffVaractorCharac},\cite{FastHighVoltageNLTL}, \cite{nikoo2018theory}, \cite{TwoLine},\cite{ComputerExpNLTL}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{EstimatingQ.png}
\caption{Transient Waveform for Estimating Q
}\label{fig:EstimatingQ}
\end{figure}

To estimate our circuit Q, we employ a technique called ring-down method
\cite{giangrandi}. Driving the circuit with a square wave much slower than the
expected resonance frequency of the LC network, we simply count the amount of
cycles it takes for the signal envelope to decay to rougly 50\% of the maximum
amplitude. Observing figure /ref{fig:EstimatingQ}, we see that the ringing dies
down in about 1 cycle. To get our Q estimate, we simply multiply this value by
approximate 4.53. This yields an approximate Q of 4.53 for our transmission
line. This seems a little lower than expected however, we can see that the
ringing is not as clean as we expected.
It is unsurprising that our non-linear circuit results in a fluctuating
impedance on the line causing reflections and is prone to generating harmonic
content.

By feeding in a 1Vpp Sine wave and measuring the frequency response of our
circuit, we see that many harmonics should be present in our line. Since we are
using this simulation to stand in place of a physical measurement, this
interferenece makes sense.

@@

While we were able to draft a preliminary Verilog-A module for this project,
we were unable to fully debug, implement, or optimize this code.
Introductory literature exists explaining how these models are constructed
and used \cite{VerilogAFun}. There also exists literature specifically gear
toward creating RF models using Verilog-A\cite{VerilogARF}.

@@

>>>>

The frequency response of our circuit effectively tells us the operating
bandwidth of our ciruit. With a 10 ladder long circuit, our cuttoff can be
calculated to be around 103Mhz. We also notice that as we near the corner, the
nonlinearities present in the circuit cause increased amounts of resonance as
expected. The thing to notice is the presence of multiple oscillations of
increasing frequency. These are frequencies we may want to consider when
measuring circuit quality factor, Q.

\begin{figure}[htb]
\centering
\includegraphics[width=0.35\textwidth,angle = -90]{ACResponseB1.png}
\caption{Simulated AC Response for Board 1}
\label{fig:simACBoard1}
\end{figure}

@@

Comparing figures \ref{fig:simACBoard1} and \ref{fig:MeasACBoard1}, we see a
similar pattern however with an additional -10dBm loss at DC and less pronounced
resonant frequencies. The additional loss could be due to the cables or due to
improper modeling of our series resistance in the line.

@@

Figure \ref{fig:SetupWBiasing} shows the lab setup used to take the time-domain
measurements. A bias-Tee is used to provide a DC bias to our NLTL and is
adjusted by a bench power supply. A picosend pulse generator is used to send
in a well-behaved high speed signal into the DUT.

The input wave is a 1Mhz 1Vpp Square wave with 10nS rise and fall times and the
bias is adjusted from 0 to 3V to further investigate its effect on the
capacitance of the varactor.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Probed_Input_N10_N240_NoSeriesResistance}
\caption{Simulated Risetimes for Input pulse, and the $240^{th}$ node}
\label{fig:probedNoResistance}
\end{figure}

Figure \ref{fig:probedNoResistance} shows the expected rise time improvement for
a circuit like ours with 240 ladders sections in an ideal environment. Once we
account for the series resistance, $Rser = -0.7\Omega$ for the purposes of
figure \ref{fig:probedWithResistance}. We see in this case the loss is great
enough to overcome the linearity of the line and we see a rise time increase
instead.

@@

Figures \ref{fig:MeasuredSquare1VBiasB1} and \ref{fig:MeasSquare2VBiasB1} show
the measured response to a square wave with $V_{dc} = 1V$ and $V_{dc} = 2V$,
respectively. While we seem some pulse sharpening in both cases, we don't see
the increase shown in figure \ref{fig:RiseVsLineVsBias}.

@@

@@

We now change the stimulus to a 1Vpp Sine wave at 1Mhz, and find the power
spectrum the NLTL output. In figure \ref{fig:SimSpec}, it is shows that as a non-linear
circuit there is a great deal of harmonic content generated due to
non-linearity.We expect to see odd and even harmonics throughout the entire
sweep.

Figure \ref{fig:MeasSpec} shows that in the lab, we don't see this same
behavior. This is puzzling and implies that either linear parasitic capacitance
is the dominant factor as a result of either the connectors, board material or
inductor contstruction, or there is enough loss in the line to linearize the
structure or both.

To further test this assumption, we can adjust the inductor model or include the
other classic parasitic components of a transmission line as shown and discussed
in \cite{nikoo2018theory}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{MeasuredSpectrum.png}
\caption{Meaured Power Spectrum of Board 1. We see a lack of the harmonics we
expected from simulation}
\label{fig:MeasSpec}
\end{figure}

@@

% \section{ Model Accuracy/ Predictions }
% Under Construction: Using this section for generating bibliography for the the
% time being. We will work on predictions and further flesh things out during the
% next revision.
% \cite{ould2011circuit} \cite{distributedAnalogPhase},\cite{ellinger2003varactor},\cite{lee2012nonlinear},\cite{UltraCompact},\cite{EffVaractorCharac},\cite{FastHighVoltageNLTL}, \cite{nikoo2018theory}, \cite{TwoLine},\cite{ComputerExpNLTL}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{EstimatingQ.png}
\caption{Transient Waveform for Estimating Q
}\label{fig:EstimQ}
\end{figure}

To estimate our circuit Q, we employ a technique called ring-down method
\cite{giangrandi}. Driving the circuit with a square wave much slower than the
expected resonance frequency of the LC network, we simply count the amount of
cycles it takes for the signal envelope to decay to rougly $50\%$ of the maximum
amplitude. Observing figure \ref{fig:EstimQ}, we see that the ringing dies
down in about 1 cycle. To get our Q estimate, we simply multiply this value by
approximate 4.53. This yields an approximate Q of 4.53 for our transmission
line. This seems a little lower than expected however, we can see that the
ringing is not as clean as we expected.
It is unsurprising that our non-linear circuit results in a fluctuating
impedance on the line causing reflections and is prone to generating harmonic
content.

By feeding in a 1Vpp Sine wave and measuring the frequency response of our
circuit, we see that many harmonics should be present in our line. Since we are
using this simulation to stand in place of a physical measurement, this
interference makes sense.

@@

While we were able to draft a preliminary Verilog-A module for this project,
we were unable to fully debug, implement, or optimize this code.
Introductory literature exists explaining how these models are constructed
and used \cite{VerilogAFun}. There also exists literature specifically geared
toward creating RF models using Verilog-A\cite{VerilogARF}.

@@

In this paper, we have summarized the work we have done in understanding the use
of NLTL's and nonlinear waves in general and attempted to reproduce these
results using simulation and measurement. While it was a good first attempt,
there are many areas to explore further such as the simulation, building and
measurement of a model dealing with higher bandwidths (0-6GHz), Non-uniform
geometry, simultaneous edge sharpening, and writing a more accurate Verilog-A
module. For much higher frequencies,the design may need to be constructing using
ADS and momentum as this neccesitates much smaller components and boards.
